\documentclass[../main.tex]{subfiles}

\begin{document}

\begingroup
\let\endtitlepage\relax
\let\vfil\relax

% Abstract
\begin{abstract}
    \par Nowadays, personal clouds are becoming more and more popular mainly thanks to the benefits it brings (availability of resources, ease of use, ease of shareability). However, a few decades ago, we never asked a very important question: what are the disadvantages of personal clouds? A few years ago, we started to realise those downsides which were most of the times related to our personal information security. Besides from that, we realised that personal cloud laked the traceability of our information, which means knowing who accessed which data at what time.
    \par The above two concepts became more and more important in modern society in part thanks to the GDPR. There is a will of the end-users to be able to control their own data. They don't want anyone else to use it for other purposes than legal ones. End-user wants their personal information to be securely stored and that none can breach their privacy.
    \par To cope with all these issues, we propose an innovative personal cloud client called LAUXUS. In this paper, we developed and proved that our client software conceals with the above-mentionned constraints. In a nutshell, we designed and developed a software that allows end-user to harness the power of personal clouds while discarding all the security issues associated with clouds.
\end{abstract}

% Acknowledgements
\let\titlepage\relax
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
    \par The first person that I would like to thank is my supervisor for its investment, throughout the entire year (even during the hard time that was the containment). I thank him a lot for taking the time to read again and again my work. Guide me with constructive and relevant feedback during the whole process to have the best outcome possible. 
    \par The second person that I thank is Igor Zavalyshyn. He very happily helped me get started with the Intel SGX development by guiding me into which resources were the most relevant and useful. He took some of his private time to help me troubleshoot issues I had for installing SGX and diagnose issues. Always responding kindly and very fast.
    \par Last, I thanks my family for its help and support. Especially my father for taking the time to discuss with me about my work (no matter the hour of the day and the day of the year) and by reading, again and again, my work.
    \par These three people are those that made this all works come to a happy ending.
\end{abstract}
\endgroup

\end{document}